### 2016-04-22 manuscript-body.tex
Fix references in itemized list of misconceptions

\begin{itemize}
\tightlist
\item
  Objects in object-oriented programming (Holland, Griffiths, \&
  Woodman, 1997)
\item
  Algorithms and data structures (Danielsiek, Paul, \& Vahrenhold, 2012;
  Paul \& Vahrenhold, 2013)
\item
  Programming statements in BASIC (Bayman \& Mayer, 1983)
\item
  Programming in Java (Fleury, 2000)
\item
  Programming in Pascal (Fleury, 1993)
\item
  Parameter-passing (Fleury, 1991)
\item
  Arrays in Java (Kaczmarczyk et al., 2010)
\item
  Objects in Java (Kaczmarczyk et al., 2010)
\item
  Algorithms and computational complexity (Trakhtenbrot, 2013)
\item
  Boolean logic (Herman et al., 2008)
\item
  The efficiency of algorithms (Gal-Ezer \& Zur, 2004)
\item
  The Build-Heap algorithm (Seppälä, Malmi, \& Korhonen, 2006)
\item
  Hashtables (Patitsas, Craig, \& Easterbrook, 2013)
\item
  The correctness of programs (Kolikant \& Mussai, 2008)
\end{itemize}

>>>>

\begin{itemize}
\tightlist
\item
  Objects in object-oriented programming \cite{holland_avoiding_1997}
\item
  Algorithms and data structures \cite{danielsiek_detecting_2012,paul_hunting_2013}
\item
  Programming statements in BASIC \cite{bayman_diagnosis_1983}
\item
  Programming in Java \cite{fleury_programming_2000}
\item
  Programming in Pascal \cite{fleury_student_1993}
\item
  Parameter-passing \cite{fleury_parameter_1991}
\item
  Arrays in Java \cite{kaczmarczyk_identifying_2010}
\item
  Objects in Java \cite{kaczmarczyk_identifying_2010}
\item
  Algorithms and computational complexity \cite{trakhtenbrot_students_2013}
\item
  Boolean logic \cite{herman_proof_2008}
\item
  The efficiency of algorithms \cite{gal-ezer_efficiency_2004}
\item
  The Build-Heap algorithm \cite{seppala_observations_2006}
\item
  Hashtables \cite{patitsas_countably_2013}
\item
  The correctness of programs \cite{kolikant_my_2008}
\item
  Polynomial and mapping reduction in the Theory and Computation of Complexity \cite{gal-ezer_identification_2016}
\end{itemize}
